```{r}
# Read data
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

**Question set 1**

1. What is the overall number of chocolate bars rated?
```{r}
summary(choco)
```

There are 1852 chocolate bars rated.

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
library(ggplot2)
ggplot(data = choco, aes(x=Review.Date)) + geom_bar()
```

The number of ratings increases until 2015 and a sharp decline occurs.

**Question set 2**

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
```{r}
ggplot(data = choco, aes(x =Rating)) + geom_histogram(bins = 20)
```

Majority of the chocolate's rating are centered around ~2.7 to ~3.6. The average rating of around 3.5 could be deferred from the graph. The histogram seems to be unimodal and shares a normal distribution.

2. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
ggplot(data = choco, aes(x = Cocoa.Pct, y = Rating)) + geom_point()
```

We can observe that the highest and lowest rating are from chocolate bar's with 70% cocoa percentage, so we can't really draw a conclusive statement from this graph alone.

```{r}
library(dplyr)
pctdata = choco %>% group_by(Cocoa.Pct) %>% summarise(count = n(), avgrate = mean(Rating))

ggplot(data = pctdata, aes(x = Cocoa.Pct, y = avgrate)) + geom_point(aes(size = count))
```

By grouping cocoa percentage and plotting their average rating, we can note that 50% cocoa percentage yields the highest rating. However, there is likely prone to error as there is a relatively small sample size for chocolate bar with 50% cocoa percentage. Such, it is inconclusive if there are correlation between cocoa percentage and ratings.

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings
```{r}
cmpcnt = choco %>% count(Company) %>% arrange(desc(n))
head(cmpcnt)

cmpdata = choco %>% filter(Company %in% c('Soma', 'Bonnat', 'Fresco'))
ggplot(data = cmpdata, aes(x = Company, y = Rating)) + geom_boxplot()
ggplot(data = cmpdata, aes(x = Rating)) + geom_bar() + facet_wrap(~Company)
```

Bonnat has percentile of its rating's around 4 which is by far the highest comparatively amongst the three company. Whereas, Soma has the highest mean rating for their chocolate with a dense collection around 3.5 and above. Fresco similarly has most of its rating averaging around 3.5, though it has lesser bars proportionately above that.

**Own question**
1. (Roy) Which location produces the bean with the highest average rating with at least 10 rating?
```{r}
beandata = choco %>% group_by(Specific.Bean.Origin) %>% summarise(count = n(), avgrate = mean(Rating)) %>% filter(count >= 10)

ggplot(data = beandata, aes(x = Specific.Bean.Origin, y = avgrate)) + geom_point(aes(size = count, color = Specific.Bean.Origin), show.legend = FALSE) + coord_flip()
```

From the plot, we can see that Porcelana produces the highest average rated beans compared to other region.

2. (Xuan Wen) Which year produces the best chocolate?
```{r}
yearRating = choco %>% group_by(Review.Date) %>% summarise(meanRating = mean(Rating))
ggplot(data = yearRating, aes(x=Review.Date, y=meanRating)) + geom_bar(stat="identity") 

yearRating_sort = yearRating%>% arrange(meanRating)
yearRating_sort$Review.Date = as.character(yearRating_sort$Review.Date)
ggplot(data = yearRating_sort, aes(x=fct_reorder(Review.Date,meanRating), y=meanRating)) + geom_bar(stat="identity") + xlab("Review.Date") + ggtitle("Mean ratings in ascending")
```

From the chart, we can say that year 2017 produces the best chocolate since it has the highest average rating.
